### 2022-08-13 doc/src/MSLevel.tex
The Privileged ISA no longer has an sideleg CSR

The value of \z{stopi} is zero unless:
(a)~there is an interrupt that is both pending in \z{sip}/\z{siph}
and enabled in \z{sie}/\z{sieh}, or, if the hypervisor extension is
implemented, both pending in \z{hip} and enabled in \z{hie}; and
(b)~if CSR \z{sideleg} or \z{hideleg} exists, the interrupt is not
delegated to a lower privilege level.
When there is a pending-and-enabled major interrupt for supervisor
level, field IID is the major identity number of the highest-priority
interrupt, and field IPRIO indicates its priority.

>>>>

The value of \z{stopi} is zero unless:
(a)~there is an interrupt that is both pending in \z{sip}/\z{siph}
and enabled in \z{sie}/\z{sieh}, or, if the hypervisor extension is
implemented, both pending in \z{hip} and enabled in \z{hie}; and
(b)~the interrupt is not delegated to a lower privilege level
(by \z{hideleg}, if the hypervisor extension is implemented),
When there is a pending-and-enabled major interrupt for supervisor
level, field IID is the major identity number of the highest-priority
interrupt, and field IPRIO indicates its priority.
